Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-19 3.phase_transitions/3.global-tests.tex
clean up repo: rename main.tex, remove unused figures, organize directories

\begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection.eps}
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection_vanishing_signals.eps}
      \caption{The phase diagrams of the sparse signal detection problem. 
      Signal size and sparsity are parametrized by $r$ and $\beta$, respectively.
      % Signal sparsity $|S|$ is parametrized by $\beta$. 
      % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($T$).
      In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
      The detection problem is unsolvable for very sparse and weak signals in the undetectable regions.
      Notice that the $L_1$ and $L_2$ statistics are in fact sub-optimal for all sparsity levels.
      On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
      The \ac{HC} statistic can detect signals in all configurations in the detectable regions; we explicitly marked the region where signals are only detectable by \ac{HC} among the statistics considered.
      See the text and Theorem \ref{thm:detection-optimality}.}
      \label{fig:phase-diagram-signal-detection}
\end{figure}

>>>>

\begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{figures/theoretical_boundaries/phase_diagram_signal_detection.eps}
      \includegraphics[width=0.7\textwidth]{figures/theoretical_boundaries/phase_diagram_signal_detection_vanishing_signals.eps}
      \caption{The phase diagrams of the sparse signal detection problem. 
      Signal size and sparsity are parametrized by $r$ and $\beta$, respectively.
      % Signal sparsity $|S|$ is parametrized by $\beta$. 
      % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($T$).
      In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
      The detection problem is unsolvable for very sparse and weak signals in the undetectable regions.
      Notice that the $L_1$ and $L_2$ statistics are in fact sub-optimal for all sparsity levels.
      On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
      The \ac{HC} statistic can detect signals in all configurations in the detectable regions; we explicitly marked the region where signals are only detectable by \ac{HC} among the statistics considered.
      See the text and Theorem \ref{thm:detection-optimality}.}
      \label{fig:phase-diagram-signal-detection}
\end{figure}

### 2021-04-19 4.exact_support_recovery/4.numerical.tex
minor update
clean up repo: rename main.tex, remove unused figures, organize directories

\begin{figure}
      \centering
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_p10000.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p100_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_Laplace_p10000_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_NLC_p10000.eps}
      \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery. 
      The experiments were repeated 1000 times for each sparsity-signal size combination, and for dimensions $p=100$ (left panels) and $p=10000$ (right panels). Numerical results agree with the boundaries described in Theorem \ref{thm:sufficient}; convergence is noticeably slower for under generalized Gaussian ($\nu=1/2$) errors.
      For reference, the dashed and dash-dotted lines represent the weak classification and detection boundaries (see Chapter \ref{chap:phase-transitions}).}
      \label{fig:phase-simulated}
\end{figure}

>>>>

\begin{figure}
      \centering
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_p10000.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_Laplace_p100_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_Laplace_p10000_4.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_NLC_p100.eps}
      \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_NLC_p10000.eps}
      \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$, from Gaussian error models (upper panels), Laplace error models (middle panels), and generalized Gaussian with $\nu=1/2$ (lower panels); darker color indicates higher probability of exact support recovery. 
      The experiments were repeated 1000 times for each sparsity-signal size combination, and for dimensions $p=100$ (left panels) and $p=10000$ (right panels). Numerical results agree with the boundaries described in Theorem \ref{thm:sufficient}; convergence is noticeably slower for under generalized Gaussian ($\nu=1/2$) errors.
      For reference, the dashed and dash-dotted lines represent the weak classification and detection boundaries (see Chapter \ref{chap:phase-transitions}).}
      \label{fig:phase-simulated}
\end{figure}

### 2021-04-19 6.URS/6.numerical.tex
clean up repo: rename main.tex, remove unused figures, organize directories

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR-05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_AR09_p10000_oracle.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Three AR(1) models with autocorrelation functions $(-0.5)^k$ (upper), 
    $0.5^k$ (middle), and $0.9^k$ (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the Bonferroni procedures (left) suffers small loss of power compared to the oracle procedures (right).
    A phase transition in agreement with the predicted boundary \eqref{eq:strong-classification-boundary} can be seen in the AR models.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.}
    \label{fig:phase-simulated-dependent}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn075_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_fGn09_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_agnostic7.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_phase_diagram_block_structure_p10000_oracle6.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Two fGn models with Hurst parameter $H = 0.75$ (upper), 
    $H = 0.9$ (middle), and the non-UDD errors in Example \ref{exmp:counter-example} (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the oracle procedures (right) is able to recover support for weaker signals than the Bonferroni procedures (left) when errors are heavily dependent, although they have the same phase transition limit.
    The non-UDD errors demonstrate qualitatively different behavior, enabling support recovery for strictly weaker signals.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.
    In the non-UDD example, dashed lines represent the limit attained by Bonferroni's procedures.
    See text for additional comments.}
    \label{fig:phase-simulated-very-dependent}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR-05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR-05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR05_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR05_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_AR09_p10000_oracle.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Three AR(1) models with autocorrelation functions $(-0.5)^k$ (upper), 
    $0.5^k$ (middle), and $0.9^k$ (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the Bonferroni procedures (left) suffers small loss of power compared to the oracle procedures (right).
    A phase transition in agreement with the predicted boundary \eqref{eq:strong-classification-boundary} can be seen in the AR models.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.}
    \label{fig:phase-simulated-dependent}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn075_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn075_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn09_p10000.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_fGn09_p10000_oracle.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_block_structure_p10000_agnostic7.eps}
    \includegraphics[width=0.4\textwidth]{./figures/simulated_boundaries/simulated_phase_diagram_block_structure_p10000_oracle6.eps}
    \caption{The empirical probability of exact support recovery from numerical experiments, as a function of sparsity level $\beta$ and signal sizes $r$. Darker colors indicate higher probability of exact support recovery. 
    Two fGn models with Hurst parameter $H = 0.75$ (upper), 
    $H = 0.9$ (middle), and the non-UDD errors in Example \ref{exmp:counter-example} (lower) are simulated.
    The experiments were repeated 1000 times for each sparsity-signal size combination.
    In finite dimensions ($p=10000$), the oracle procedures (right) is able to recover support for weaker signals than the Bonferroni procedures (left) when errors are heavily dependent, although they have the same phase transition limit.
    The non-UDD errors demonstrate qualitatively different behavior, enabling support recovery for strictly weaker signals.
    The boundaries (solid, dashed, and dash-dotted lines) are as in Fig \ref{fig:phase-simulated}.
    In the non-UDD example, dashed lines represent the limit attained by Bonferroni's procedures.
    See text for additional comments.}
    \label{fig:phase-simulated-very-dependent}
\end{figure}

### 2021-04-19 7.GWAS/7.GWAS-phase-transitions.tex
clean up repo: rename main.tex, remove unused figures, organize directories

\begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p4.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e2.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_p1e6.png} \includegraphics[width=0.49\textwidth]{OR-RAF_plots/OR-RAF_BC_study.png}
      \caption{The OR-RAF diagram visualizing the marginal power of discovery in genetic association studies, after applying Bonferroni's procedure with nominal FWER at $5\%$ level. Sample sizes are marked in each panel, and the problem dimensions are, respectively, $p=4$ (upper-left), $p=10^2$ (upper-right), and $p=10^6$ (lower-left), so that $n/\log{p}$ are roughly constant. Red curves mark the boundaries ($r=1$) of the phase transition for the exact-approximate support recovery problem; dashed curves are the equi-signal (equi-power) curves. The phase transition in signal sizes $\lambda$ translates into the phase transition in terms of $(f,R)$, and sharpens as $p\to\infty$; see Example \ref{exmp:OR-RAF_phase_transition}. In the lower-right panel, we visualize discovered associations (blue circles) in a recent GWA study (Michailidou et al. (2017)); the estimated odds ratios and risk allele frequencies are subject to survival bias and should not be taken at their face values; see Remark \ref{rmk:OR-RAF_false_evidence}.
      } 
      \label{fig:OR-RAF_GWAS}
\end{figure}

>>>>

\begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p4.png}
      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p1e2.png}
      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_p1e6.png}
      \includegraphics[width=0.49\textwidth]{figures/OR-RAF_plots/OR-RAF_BC_study.png}
      \caption{The OR-RAF diagram visualizing the marginal power of discovery in genetic association studies, after applying Bonferroni's procedure with nominal FWER at $5\%$ level. Sample sizes are marked in each panel, and the problem dimensions are, respectively, $p=4$ (upper-left), $p=10^2$ (upper-right), and $p=10^6$ (lower-left), so that $n/\log{p}$ are roughly constant. Red curves mark the boundaries ($r=1$) of the phase transition for the exact-approximate support recovery problem; dashed curves are the equi-signal (equi-power) curves. The phase transition in signal sizes $\lambda$ translates into the phase transition in terms of $(f,R)$, and sharpens as $p\to\infty$; see Example \ref{exmp:OR-RAF_phase_transition}. In the lower-right panel, we visualize discovered associations (blue circles) in a recent GWA study (Michailidou et al. (2017)); the estimated odds ratios and risk allele frequencies are subject to survival bias and should not be taken at their face values; see Remark \ref{rmk:OR-RAF_false_evidence}.
      } 
      \label{fig:OR-RAF_GWAS}
\end{figure}

### 2021-04-19 7.GWAS/7.numerical.tex
clean up repo: rename main.tex, remove unused figures, organize directories

\begin{figure}
	\centering
	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu1_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}

	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu2_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}

	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu3_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}

	\includegraphics[width=0.32\textwidth]{sim_strong_boundary/simulated_strong_boundary_chi-squared_nu6_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
    \includegraphics[width=0.32\textwidth]{sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
	\caption{The empirical risks of exact, approximate, and approximate-exact support recovery (left to right) in the chi-squared model \eqref{eq:model-chisq} with Bonferroni's procedure and the Benjamini-Hochberg procedure. 
		We display results as a heatmap for $\nu=1, 2, 3, 6$ (first to last row) at dimension $p=10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
		The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher probability of exact support recovery.  
		Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.} 
	\label{fig:phase-simulated-chi-squared}
\end{figure}

@@

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p1000.eps}
      % \includegraphics[width=0.33\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p10000.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical probability of exact support recovery of Bonferroni's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') in the additive Gaussian error model and under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-exact-boundary}; regions where asymptotically exact support recovery can be achieved are shaded in grey.
      The difference in power between Bonferroni's procedure and the oracle procedure, as well as in the two types of alternatives both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-exact_support_recovery}
\end{figure}

@@

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p1000.eps}
      \includegraphics[width=0.32\textwidth]{sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical risk of approximate support recovery of Benjamini-Hochberg's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') and in the additive Gaussian error model under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-approx-boundary}; regions where asymptotically approximate support recovery can be achieved are shaded in grey.
      The difference in risks between Benjamini-Hochberg's procedure and the oracle procedure, as well as in the two types of alternatives, both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-approx_support_recovery}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu1_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu1_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu1_p10000.eps}

	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu2_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu2_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu2_p10000.eps}

	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu3_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu3_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu3_p10000.eps}

	\includegraphics[width=0.32\textwidth]{figures/sim_strong_boundary/simulated_strong_boundary_chi-squared_nu6_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_weak_boundary/simulated_weak_boundary_chi-squared_nu6_p10000.eps}
    \includegraphics[width=0.32\textwidth]{figures/sim_approx-exact_boundary/simulated_approx-exact_boundary_chi-squared_nu6_p10000.eps}
	\caption{The empirical risks of exact, approximate, and approximate-exact support recovery (left to right) in the chi-squared model \eqref{eq:model-chisq} with Bonferroni's procedure and the Benjamini-Hochberg procedure. 
		We display results as a heatmap for $\nu=1, 2, 3, 6$ (first to last row) at dimension $p=10^4$ (left to right column), for a grid of sparsity levels $\beta$ and signal sizes $r$.
		The experiments were repeated 1000 times for each sparsity-signal size combination; darker color indicates higher probability of exact support recovery.  
		Numerical results are in general agreement with the boundaries described in Theorem \ref{thm:chi-squared-exact-boundary}; for large $\nu$'s, the phase transitions take place somewhat above the predicted boundaries.} 
	\label{fig:phase-simulated-chi-squared}
\end{figure}

@@

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p1000.eps}
      % \includegraphics[width=0.33\textwidth]{sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p10000.eps}
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/exact_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical probability of exact support recovery of Bonferroni's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') in the additive Gaussian error model and under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-exact-boundary}; regions where asymptotically exact support recovery can be achieved are shaded in grey.
      The difference in power between Bonferroni's procedure and the oracle procedure, as well as in the two types of alternatives both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-exact_support_recovery}
\end{figure}

@@

\begin{figure}
      \centering
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100.eps}
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p1000.eps}
      \includegraphics[width=0.32\textwidth]{figures/sim_one-vs-two-sided/approx_recovery_one-vs-two-sided_beta06_p100000.eps}
      \caption{The empirical risk of approximate support recovery of Benjamini-Hochberg's procedure (solid curves) and the oracle procedure (dashed curves) in the chi-squared model with one degree of freedom (marked `2') and in the additive Gaussian error model under one-sided alternatives (marked `1'). 
      We simulate at dimensions $p=10^2, 10^3, 10^5$ (left to right) for a grid of signal sizes $r$ and sparsity level $\beta=0.6$.
      The experiments were repeated 1000 times for each method-model-signal-size combination. 
      Numerical results show evidence of convergence to the 0-1 law as predicted by Theorem \ref{thm:chi-squared-approx-boundary}; regions where asymptotically approximate support recovery can be achieved are shaded in grey.
      The difference in risks between Benjamini-Hochberg's procedure and the oracle procedure, as well as in the two types of alternatives, both decrease as dimensionality increases.} 
      \label{fig:one-vs-two-sided-approx_support_recovery}
\end{figure}
